Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-10 paper/main.tex
added a description of feature clustering scores (uncorrected)

\paragraph*{Clustering scores (uncorrected).}

\paragraph*{Permutation-corrected clustering scores.}

>>>>

\paragraph*{Feature clustering scores (uncorrected).}

Feature clustering describes a participant’s tendency to recall similar
presented items together in their recall sequences, where ``similarity''
considers one given feature dimension (e.g., category, color, etc.). Computing
the clustering score for one feature dimension starts by considering those
feature values from the first word the participant recalled on the list. Next,
we sort all not-yet-recalled words in ascending order according to their
feature-based distance to the just-recalled item (see \textit{Defining
feature-based distances}). We then compute the percentile rank of the observed
next recall. We averaged these percentile ranks across all of the participant’s
recalls for the current list to obtain a single uncorrected clustering score
for the list, for the given feature dimension. We repeat this process for each
feature dimension in turn to obtain a single uncorrected clustering score for
each list, for each feature dimension.

\paragraph*{Permutation-corrected feature clustering scores.}
